About

### 2024-09-07 about.qmd
Add authors, license and funding note

---
title: "About"
bibliography: grateful-refs.bib
---

@@

@@

>>>>

---
title: "About"
author:
  - name: "Florian Kohrt"
    orcid: "0000-0003-0374-5625"
  - name: "Josephine Zerna"
    email: "josephine.zerna@tu-dresden.de"
    orcid: "0000-0003-2892-884X"
  - name: "Christoph Scheffel"
    email: "christoph_scheffel@tu-dresden.de"
    orcid: "0000-0001-5963-9229"
bibliography: grateful-refs.bib
---

# Utilized Software

@@

```{r}
#| class.output: "txt code-overflow-scroll"

@@

# License and Disclaimer

If not indicated otherwise, this tutorial is licensed under [CC\ BY\ 4.0](https://creativecommons.org/licenses/by/4.0/). None of the discussion in this tutorial constitutes legal advice.

Any screenshots of [RStudio](https://github.com/rstudio/rstudio) are released under the [GNU Affero General Public License v3](https://www.gnu.org/licenses/gpl-3.0.html).

```{.txt .code-overflow-wrap}
Copyright (C) 2024 Posit Software, PBC

This program is free software: you can redistribute it and/or modify it under the terms of version 3 of the GNU Affero General Public License as published by the Free Software Foundation.

This program is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the GNU Affero General Public License for more details.

You should have received a copy of the GNU Affero General Public License along with this program.  If not, see <https://www.gnu.org/licenses/>.
```

# Funding

::: {.column-margin}
![](images/bitss.png){width=250px}
:::

This work was partly funded by the Berkeley Initiative for Transparency in the Social Sciences (BITSS), managed by the Center for Effective Global Action (CEGA).
